I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-27 Paper/experiments.tex
main

Next, we shift focus to the comparison with ($\alpha$)$\beta$-CROWN, where we observe intriguing trade-offs. On the shallowest DNNs (5 layers, $5 \times 100$, $5 \times 200$), \toolname accuracy is close to $\beta$-CROWN, within 1.5\%. This is because RefinedBaB used by $\beta$-CROWN, used by 
$\beta$-CROWN, has the time to refine most of the nodes, and thus the number of branches BaB has to explore is small enough.

As network sizes increase, \toolname demonstrates better accuracy in comparison to $\beta$-CROWN. As expected, there's a trade-off between runtime and accuracy: \toolname can verify more images, albeit at the cost of increased computation time. However, more often than not, our primary concern lies in running a tool for a fixed timeout to determine whether it can verify the desired property within that time.

>>>>

Next, we shift focus to the comparison with ($\alpha$)$\beta$-CROWN, where we observe intriguing trade-offs. On the shallowest DNNs (5 layers, $5 \times 100$, $5 \times 200$), \toolname accuracy is close to $\beta$-CROWN, within 1.5\%. Here, RefinedBaB used by $\beta$-CROWN, has the time to refine most of the nodes, and thus the number of branches BaB has to explore is small enough that its very accurate.

As network sizes increase, \toolname demonstrates better accuracy in comparison to $\beta$-CROWN. For instance, for $8 \times 100$ and $8 \times 200$, 
RefinedBaB used by $\beta$-CROWN can only consider half of the layers. 
On many images, there are too many branches for BaB left to consider, and it times out,
reason why we close the gap of undetermined images from $17.6\%$ ($\beta$-CROWN) to $10.4\%$ (\toolname) in $8 \times 200$.

As expected, there's a trade-off between runtime and accuracy: \toolname can verify more images, albeit at the cost of increased computation time. However, more often than not, our primary concern lies in running a tool to determine whether it can verify the desired property within a reasonable time.

The last network $6 \times 500$ (trained naturally) is the largest one. Results were not reported in \cite{crown,prima}. On this larger network, the refined strategy of PRIMA and $\alpha,\beta$-CROWN is questionable, as the number of binary variables to encode even the first few layers is very large, and the efficiency of MILP unclear. As a matter of fact, refinedBaB is "NotImplemented" in $\alpha,\beta$-CROWN for this network, and the results are 
surprisingly inaccurate and fast in PRIMA (even faster than for $5 \times 100$), probably because few/no nodes are actually refined. We reported the standard pureBaB setting of $\alpha,\beta$-CROWN instead, with the usual 30s associated timeout. Accuracy on $\alpha,\beta$-CROWN was also very low, only $15\%$ more images verified than DeepPoly. To understand the impact of runtime, we also experimented with a 2000s timeout for $\alpha,\beta$-CROWN. It only improves the accuracy by $3.5\%$, at $44.5\%$, with a runtime of $954s$ ($50$ times longer than with the original $30s$ timeout). We conclude that the number of branches is often too high for $\alpha,\beta$-CROWN to tackle such a hard DNN.
For comparison, \toolname could verify more than $20\%$ more images than
even $\alpha,\beta$-CROWN with the longest timeout, taking less than $0.3s$ per neuron to perform the verification in average per image.
